---
output: html_document
---
Importing the Dataset
```{r}
df = read.csv('/Users/imuminov/OneDrive/School/MSITM/MSBA320/FinalProject/dataset.csv', header = TRUE)
attach(df)
names(df)
head(df)
```
```{r}
summary(df)
```

```{r}
hist(Charges, ylab = "Frequency", col = "blue",breaks = 30)
```

```{r}
library(tidyverse)
ggplot(df,aes(x = Charges, color = Smoking))+
  geom_histogram(fill = "white", position = "dodge")+
  theme(legend.position = "top")
```

```{r}
ggplot(df)+
  geom_violin(mapping = aes(x = Smoking, y = Charges, fill = Gender), draw_quantiles = (c(0.25,0.5,0.75)))

```
```{r}
ggplot(df)+
  geom_point(mapping = aes(x = Age, y = Charges, colour = Smoking))
```
```{r}
ggplot(df,aes(x = BMI))+
  geom_histogram(fill = "blue", position = "dodge")+
  theme(legend.position = "top")
```
```{r}
ggplot(df)+
  geom_point(mapping = aes(x = BMI, y = Charges))
```

```{r}
bg<-ggplot(df, aes(children))
bg+geom_bar(fill = "blue")
```

```{r}
p<-ggplot(df, aes(children,y = Charges, group = children))
p+geom_boxplot(fill = "white", color = "blue")
```
```{r}
df$Gender = as.numeric(df$Gender)
df$Smoking = as.numeric(df$Smoking)
df$Region = as.numeric(df$Region)
```
```{r}
library(corrplot)
costCorr<-cor(df)
```


```{r}
corrplot(costCorr, method = "pie")
```
Before we perform independent two-sample T-test to check the mean difference in charges for smokers and non-smokers, we will look at the boxplot of those variables. The boxplot shows that smokers and non-smokers have unequal variances, so in the t-test we will set the parameter as unequal variances. 
```{r}
boxplot(Charges ~ Smoking)
```
Let's perform the t-test. 
1. Our Null Hypothesis is that Charges of smokers and non-smokers have equal means. 
2. Alternative Hypothesis is Charges for smokers and non-smokers' means are not equal.
3. We perform 2 sided test, because we have equal sign. 
4. We take confidence interval of 95%. 

```{r}
?t.test
```
```{r}
t.test(Charges~Smoking, mu = 0, alt = "two.sided",conf.level = 0.95, var.equql = FALSE)
```

```{r}
boxplot(Charges~Gender)
```
```{r}
t.test(Charges~Gender, mu = 0, alt = "two.sided",conf.level = 0.95, var.equql = FALSE)
```
One-way ANOVA, Region independent variable. 
```{r}
df$Region = as.factor(df$Region)
levels(Region)
```

```{r}
df = read.csv('/Users/imuminov/OneDrive/School/MSITM/MSBA320/FinalProject/dataset.csv', header = TRUE)
reg<-ggplot(df,aes(x = Region, y = Charges, fill = Region))
reg + geom_boxplot()
```
One-Way anova for Region Variable
```{r}
oneWay<-aov(Charges~Region)
summary(oneWay)
```
Multiple Linear Regression
First Model. In the first model, we take three independent variables, Age, BMI and Smoking. 
```{r}
fit<-lm(Charges~Age + BMI + Smoking)
summary(fit)
plot(fit)
car::vif(fit)
```
```{r}
car::vif(fit)
```
```{r}
library(MASS)
sresid<-studres(fit)
hist(sresid, main = "Distribution of Studentized Residuals",breaks = 40, xlab = "Studentized Residuals")
```


```{r}
fit<-lm(Charges~Age + BMI + Smoking)
fit2<-lm(Charges~Age+BMI+Smoking+children)
anova(fit,fit2)
```
```{r}
fit2<-lm(Charges~Age+BMI+Smoking+children)
summary(fit2)
```






















